---
title: "Data_607_Assignment3"
author: "Mohamed Hassan-El Serafi"
date: "2023-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(stringr)
```


Please deliver links to an R Markdown file (in GitHub and rpubs.com) with solutions to the problems below.  You may work in a small group, but please submit separately with names of all group participants in your submission.


### 1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
df <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv")
df
```


```{r}
glimpse(df)
colnames(df)
df
```

```{r}
new_df<- df[grep("DATA|STATISTICS", df$Major),]
new_df
```


### 2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"


Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")




```{r}
string_list = c('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"')
string_list
```

```{r}
new_string_list <- str_extract_all(string_list, "\\w[a-z]+\\s?[a-z]+\\w")
print(new_string_list)
```

```{r}
new_list <- gsub('[[:digit:]]+', '', new_string_list)
new_list
```


```{r}
class(new_list)
```


```{r}
cat(str_c(new_list, collapse = " , "))
```


The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:


### 3. Describe, in words, what these expressions will match:

(.)\1\1 

This expression would throw an error, since it's missing double quotes and a backslash.

```{r}
test_set <- c('aaa','bbbght','abba','1221','xyzzyx','zrzrzlk','53575','abaza','1234djakfl;jdafkjad4321','abccba', "$%^^%$#@*")
str_match(test_set, "(.)\1\1")
```


"(.)(.)\\2\\1"

This expression would produce two characters followed by the same characters in reverse order. An example is "abba".

```{r}
str_match(test_set, "(.)(.)\\2\\1")
```


(..)\1

This expression would throw an error, since it's missing double quotes and a backslash.

```{r}
str_match(test_set, "(..)\1")
```


"(.).\\1.\\1"

This expression produces characters that are repeated 3 or more times within a group of characters.

```{r}
str_match(test_set, "(.).\\1.\\1")
```


"(.)(.)(.).*\\3\\2\\1"

This expression would produce a group where a string of 3 or more characters also appear in reverse order anywhere in the group.


```{r}
str_match(test_set, "(.)(.)(.).*\\3\\2\\1")
```


### 4. Construct regular expressions to match words that:
Start and end with the same character.
Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
# Start and end with the same character
variable_set <- c("test", "high", "stuff", "lawn", "abra")
str_extract(variable_set, "^(.).*\\1$")
```


```{r}
# Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
testing_set <- c("trial", "church", "mile", "pepper")
str_match(testing_set, "(..).*\\1")
```


```{r}
# Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
variable_test_set <- c("model", "eleven", "pepper", "train", "mississippi")
str_extract(variable_test_set, "([a-z]).*\\1.*\\1")
```

